Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-18 paper/icml_drau/framework.tex

In what follows, a formalized view of near continuous environments is
given, along with $\deltat$ dependant definitions of return, discount
factor and value functions that are shown to converge to well defined
continous time limits. Finally, it is shown that the state-action value
function collapses to the value function as $\deltat$ goes to $0$.
Consequently there is no Q-learning in continuous time, foreshadowing
problematic behaviors of near continuous time Q-learning.
%      \TODO{We should explain somwhere here that, if not invariant,
%      harder to find good hyperparameters} DONE

>>>>

A formalized view of near continuous environments is
given below, along with $\deltat$-dependent definitions of return, discount
factor and value functions, that converge to well defined
continous-time limits. The state-action value
function is shown to collapse to the value function as $\deltat$ goes to $0$.
Consequently there is no Q-learning in continuous time, foreshadowing
problematic behaviors of near continuous time Q-learning.
%      \TODO{We should explain somwhere here that, if not invariant,
%      harder to find good hyperparameters} DONE
